\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-27 paper.tex
'frameinterpolation2'

@@

\subsection{Results}
\subsection{Analysis}
Illustrate why Approximate Code achieve high reliability with low cost
\section{Conclusion}
\section*{Acknowledgment}

\bibliographystyle{IEEEtrans}
\bibliography{paper}

>>>>

\subsection{Video Frame Recovery: Frame Interpolation}
In the circumstance of data loss, it's common to lose some frames and then the video is not complete. One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates. Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.

Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames. This is a technique that can model natural motion within a video, and generate frames according to this modelling. Artificially increasing the frame-rate of videos enables the possibility of frame recovery. Optical flow is commonly addressed in the video frame interpolation problem. Optical flow is the pattern of apparent motion of objects, surfaces, and edges in a visual scene caused by the relative motion between an observer and a scene. Video frame interpolation algorithms typically estimate optical flow or its variations and use them to warp and blend original frames to produce interpolation results.

Recently, phase-based methods have shown promising results in applications such as motion and view extrapolation \cite{b1}\cite{b2}\cite{b3}. These methods rely on the assumption that small motions can be encoded in the phase shift of an individual pixel¡¯s color. Meanwhile, deep learning approaches, and in particular Convolutional Neural Networks (CNNs), have set up new state-of-the-art results across many computer vision problems which also makes big improvements to frame interpolation. In neural networks, optical flow features are trained in a supervised setup mapping two frames to their ground truth optical flow field\cite{b6}\cite{b7}. Among them, a multi-scale network\cite{b4} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{b5} have so far produced the best results in terms of PSNR and middlebury benchmark respectively.

All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle). However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames. Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.

@@

\subsection{Results}
\subsection{Analysis}
Illustrate why Approximate Code achieve high reliability with low cost
\section{Conclusion}
\section*{Acknowledgment}
\begin{thebibliography}{00}
\bibitem{b1} Piotr Didyk, Pitchaya Sitthi-Amorn, William T. Freeman, Fr¨¦do Durand, Wojciech Matusik
Joint View Expansion and Filtering for Automultiscopic 3D Displays
ACM Transactions on Graphics 32(6) (Proceedings SIGGRAPH Asia 2013, Hong Kong), 2013
\bibitem{b2} Neal Wadhwa, Michael Rubinstein, Fr¨¦do Durand, and William T. Freeman. 2013. Phase-based video motion processing. ACM Trans. Graph. 32, 4, Article 80 (July 2013), 10 pages. DOI: https://doi.org/10.1145/2461912.2461966
\bibitem{b3} Meyer, Simone et al. ¡°Phase-based frame interpolation for video.¡± 2015 IEEE Conference on Computer Vision and Pattern Recognition (CVPR) (2015): 1410-1418.
\bibitem{b4} Joost van Amersfoort, Joost $\&$ Shi, Wenzhe $\&$ Acosta, Alejandro $\&$ Massa, Francisco $\&$ Totz, Johannes $\&$ Wang, Zehan $\&$ Caballero, Jose. (2017). Frame Interpolation with Multi-Scale Deep Loss Functions and Generative Adversarial Networks.
\bibitem{b5} Niklaus, Simon $\&$ Liu, Feng. (2018). Context-aware Synthesis for Video Frame Interpolation.
\bibitem{b6} Fischer, Philipp et al. ¡°FlowNet: Learning Optical Flow with Convolutional Networks.¡± 2015 IEEE International Conference on Computer Vision (ICCV) (2015): 2758-2766.
\bibitem{b7} Ilg, Eddy Mayer, Nikolaus Saikia, Tonmoy Keuper, Margret Dosovitskiy, Alexey Brox, Thomas. (2016). FlowNet 2.0: Evolution of Optical Flow Estimation with Deep Networks.
\end{thebibliography}
\bibliographystyle{IEEEtrans}
